Treatment Outcome Visualization

### 2023-10-12 Treatment_Outcomes.Rmd
RCI treatment response figures.

AnxDep_PrePost <- data.frame(cbind(Mothership_post$ID1,
                                  Mothership_post$Disorder_Type,
                                  Mothership_post$CUDOS_pre,
                                  Mothership_post$CUDOS_post,
                                  Mothership_post$CUXOS_pre,
                                  Mothership_post$CUXOS_post)) %>%
  filter(!is.na(Mothership_post$Disorder_Type))

>>>>

AnxDep_PrePost <- data.frame(cbind(Mothership_post$ID1,
                                  Mothership_post$Disorder_Type,
                                  Mothership_post$pre_anx,
                                  Mothership_post$post_anx,
                                  Mothership_post$pre_dep,
                                  Mothership_post$post_dep)) %>%
  filter(!is.na(Mothership_post$Disorder_Type))
